
\cvsection{SKILLS}
\cvskill{AWS, Serverless, Node.js}{5}
\cvskill{CI/CD, TypeScript, Container}{4}
\cvskill{Go, Vue.js, React.js, Terraform}{3}


\cvsection{Projects}
\cvproject{Precium Wallet}
    \begin{itemize}
        \item URL: https://wallet.precium.io
        \item Built cloud infrastructure using AWS.
        \item Adopted Serverless Architecture using AWS Lambda(Node.js).
        \item Built and established the frontend structure using Vue.js.
        \item Assisted in connecting to ethereum network using Web3 library.
        \item Built CI/CD pipeline using CircleCI.
    \end{itemize}
\smallskip
\cvproject{COCOIN}
    \begin{itemize}
        \item URL: https://bit.ly/COCOIN
        \item Migrated the Web Application to TypeScript from JavaScript.
        \item Migrated RDS MySQL to Amazon Aurora MySQL.
        \item Utilized Firebase to adopt Oauth2.0 and Analyze users.
        \item Built Serverless Architecture migrated from Load Balancer and Computing Instances Architecture.
        \item Optimized queries working on MySQL.
        \item Built data pipeline on AWS for the statistics.
        \item Designed the cost-effective AWS architecture(40\% cost down).
    \end{itemize}
\smallskip
\cvproject{The Backend}
    \begin{itemize}
        \item URL: https://thebackend.io
        \item Built the architecture based on docker container.
        \item Built CI/CD pipelines using AWS CodeDeploy and Jenkins.
        \item Built and established the frontend structure using React.js.
        \item Designed the schema on Amazon DynamoDB scaling out for million users.
        \item Developed web applications as a backend engineer.
    \end{itemize}
\smallskip


\cvsection{Writings}
    \begin{itemize}
        \item {Realtime analysis search keywords on potal with Serverless Architecture}\newline{- Micro Software 395(Jan. 2019)}
        \item {Serverless Hands-on part.1(Builing Todo app and web crawler using Serverless)} \newline {- Hanbit media(Apr. 2019)}
    \end{itemize}
\smallskip
